---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GFLglm v0.1.0

<!-- badges: start -->
<!-- badges: end -->

This package gives generalized fused Lasso estimator for generalized linear models via coordinate descent algorithm.
Furthermore, this package includes the R package [GFLlogit](https://github.com/ohishim/GFLlogit).

**cite this package of the latest version**:  
Ohishi, M. (2024).
GFLglm: Generalized fused Lasso for grouped data in generalized linear models.
R package version 0.1.0.
https://github.com/ohishim/GFLglm

## Installation

You can install the current version of `GFLglm` like so:

``` {r eval=F}
devtools::install_github("ohishim/GFLglm")
```

## Example

```{r echo=F, message=F, warning=F}
devtools::load_all()
```

This example requires the following packages:

```{r example, eval=F}
library(GFLglm)
library(magrittr)
```

This package has the dataset `crimetko` used in Ohishi (2024) like this

```{r}
head(crimetko)
```

The `crime` is the number of crimes of which the original data was collected by the Metropolitan Police Department, available at TOKYO OPEN DATA (https://portal.data.metro.tokyo.lg.jp/).
This variable is arranged and used the following production:   

- Tokyo Metropolitan Government & Metropolitan Police Department. The number of recognized cases by region, crime type, and method (yearly total; in Japanese), https://creativecommons.org/licenses/by/4.0/deed.en.  

The `pop` is population of which the original data was obtained from the results of the population census, as provided in e-Stat (https://www.e-stat.go.jp/en).
This variable is arranged and used.

This package also has the dataset `adj` of adjacent relationship of groups in `crimetko` like this
```{r}
head(adj)
```

For example, group 1 is adjacent to groups 2, 3, 4, 5, 6, 54, ... For such a data, Poisson regression with generalized fused Lasso can be executed as
```{r eval=F}
y <- crimetko$crime                           # the response variable  
group <- crimetko$group                       # group id
D <- adj %$% split(adj, g)                    # adjacent relationship
q <- crimetko$pop %>% inset(.==0, 1) %>% log  # offset for log-link

res <- GFLglm(y, group, D, "Poisson", offset=q)
```

The fourth parameter specifies the error distribution which can take "Gaussian", "Binomial", "Poisson", "Negative.Binomial" (or "NB"), "Gamma", or "Inverse.Gaussian" (or "IG").
For "Gamma", "NB", and "IG", there is a option using log-link by setting `link = "log"`.

## Reference

1. Ohishi, M. (2024).
Generalized fused Lasso for grouped data in generalized linear models.
*Hiroshima Statistical Research Group Technical Report*, TR-No. 24-02, Hiroshima University.
[[PDF](http://www.math.sci.hiroshima-u.ac.jp/stat/TR/TR24/TR24-02.pdf)]
